Supporting Information

### 2022-10-07 Manuscript/Supplementary_Material/Supporting_information_Journal_of_Animal_Ecology.Rmd
supp mat update

**Figure S2** Over and under-estimated motif frequencies.

**Figure S3** Over and under-estimated groups on motif positions.

@@

**Figure S6** Association between the percentile and specificity of the different plant and floral visitor groups on motif positions.

**Figure S7** Association between the percentile and number of indirect interactions of the different plant and floral visitor groups on motif positions.

**Figure S8** Frequency of floral visitor groups and number of indirect interactions per motif positions.

**Figure S9** Frequency of plant groups and number of indirect interactions per motif positions.

@@

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S3.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
kable_styling(full_width = T,latex_options = c("striped")) %>%
add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
    column_spec(c(1,4), bold = T) %>% row_spec(0, bold=T)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S2.** Comparison of motif frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al. (2020) without considering singletones. This is shown with the mean percentage of motif frequencies in empirical networks that were over the motif frequencies of the simulated ones (percentiles). This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different motif positions after removing non-robust links (singletones). The different motif positions are dividied by the average path length clasification determined by Simmons et al. (2020). The superior dendrogram indicates the differences across groups with the more separated groups showing larger differences."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S4.** Plant functional group composition separated in qualitative and quantitative variables. Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group. Plot B) shows the radar plot of the different quantitative variables standardise on the same scale also coloured with the same patterns of colours as qualitative variables per cluster or functional group. Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile (see main text) and specialization of the different plant and floral visitor groups on motif positions. Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor groups on motif positions. Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S9.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

>>>>

**Figure S2** Over and under-estimated network subgraphs frequencies.

**Figure S3** Over and under-estimated functional groups on network subgraphs positions.

@@

**Figure S6** Association between the percentile and specificity of the different plant and floral visitor functional groups on network subgraph positions.

**Figure S7** Association between the percentile and number of indirect interactions of the different plant and floral visitor functional groups on network subgraph positions.

**Figure S8** Frequency of floral visitor functional groups and number of indirect interactions per network subgraph positions.

**Figure S9** Frequency of plant functional groups and number of indirect interactions per network subgraph positions.

@@

kbl(dat, booktabs = T, linesep = "\\addlinespace", escape = FALSE, align = c("c","l","c","c","l","l","c"),caption = "\\textbf{Table S3.} Traits used to delimit the different plant functional groups divided in quantitative and categorical traits.") %>%
kable_styling(full_width = T,latex_options = c("striped")) %>%
add_header_above(c("Quantitative traits" = 2,"Categorical traits" = 2),bold=T)  %>%
    column_spec(c(1,3), bold = T) %>% row_spec(0, bold=T)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=4.5,fig.height=6.5, fig.cap="**Figure S2.** Comparison of network subgraph frequencies between empirical and simulated networks grouped by average path length (plots a, b, c and d) as determined in Simmons et al. (2020) without considering singletones. This is shown with the mean percentage of network subgraph frequencies in empirical networks that were over the subgraph frequencies of the simulated ones (percentiles). This was done by network (light blue dots) and then averaged for all networks (black dots with error bars that correspond to the standard deviation)."}
library(lme4)
library(nlme)
library(tidyverse)
source("../../Scripts/Scripts_Alfonso/add_study_id.R")
d <- read_csv("../../Data/Csv/Motifs_frequencies_and_null_models_NOSING/Motifs_frequency_percentile_NOSING.csv")
d <- add_study_id(d)
#str(d)
#head(d)

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.height=8,fig.width=8,fig.align = 'center', fig.cap="\\textbf{Figure S3.} Heatmap indicating under- and over- representation of pollinator and plant functional groups in the different network subgraph positions after removing non-robust links (singletones). The different subgraph positions are dividied by the average path length clasification determined by Simmons et al. (2020). The superior dendrogram indicates the differences across functional groups with the more separated groups showing larger differences."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE,fig.height=7, fig.width=12, fig.cap="**Figure S4.** Plant functional group composition separated in qualitative and quantitative variables. Panel A) shows the percentage of the different categories within trait represented with different colours for each functional group. Plot B) shows the radar plot of the different scaled quantitative variables. Both quantitative and qualitative variables are coloured with the same pattern of colours by functional group. Group 1 corresponds to short-lived selfers; group 2 to small outcrossing perennials; group 3 to self-incompatible perennials with large flowers; group 4 to tall plants with small unisexual flowers; and, group 5 to short-lived outcrossers with long zygomorphic flowers."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%',  fig.cap="\\textbf{Figure S6.} Association between the percentile (see main text) and specialization of the different plant and floral visitor functional groups on network subgraph positions. Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE,fig.align="center", fig.width=14,fig.height=7, out.width='100%', fig.cap="\\textbf{Figure S7.} Association between the percentile (see main text) and number of indirect interactions of the different plant and floral visitor functional groups on network subgraph positions. Here we consider that percentiles above 0.75 indicate over-representation and percentiles below 0.25 under-representation in the comparison between empirical and simulated networks."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S8.} Frequency of the different floral visitor functional groups on the different network subgraph positions aggregated by the number of indirect interactions for the different subgraph positions."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S9.} Frequency of the different plant functional groups on the different network subgraph positions aggregated by the number of indirect interactions for the different subgraph positions."}
